Verifying Demonstrations

### 2021-06-16 paper/security-properties.tex
Updates data in adversary model

    \item\label{TemporallyRelated} \emph{Temporal eligibility}: demonstrate that the proof was created after the start of the protest and before the end of the protest.
      \Ie \(t\subseteq t_\prtst\) in \cref{ValidProofShare}.

    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: demonstrate that the proof is spatially related to the physical location or journey of the protest.
      \Ie \(l\subseteq l_\prtst\) in \cref{ValidProofShare}.

@@

For privacy, we require a set of unlinkability properties:%
\label{privacy-properties}
\begin{requirements}[P]
\item\label{PseudonymUnlink} \emph{Pseudonym unlinkability}: given a protest 
  (identifier \cid), protesters Alice and Bob, and a pseudonym \(\pid_b\), the 
  adversary cannot tell if \(\pid_b = \pid_{\text{Alice}}\) or \(\pid_b = 
    \pid_{\text{Bob}}\), except with negligible probability. And similarly with $wid$ if Alice and Bob act as witnesses.
\item\label{ProtestUnlink} \emph{Protest unlinkability}: protesters' pseudonyms 
  (\(\pid_\cid, \pid_{\cid'}\)) must be unlinkable between protests (\(\cid, 
    \cid'\)) from the adversary's perspective.
\item\label{WitnessUnlink}\emph{Witness unlinkability}:  witnesses' pseudonyms 
  (\(\wid_\pid, \wid_{\pid'}\)) must be unlinkable between protesters (\(\pid, 
    \pid'\)) from the adversary's perspective.
\end{requirements}

>>>>

    \item\label{TemporallyRelated} \emph{Temporal eligibility}: demonstrate that the proof was created after the start of the protest and before the end of the protest.
      \Ie \(t\subseteq t_{\prtst}\) in \cref{ValidProofShare}.

    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: demonstrate that the proof is spatially related to the physical location or journey of the protest.
      \Ie \(l\subseteq l_{\prtst}\) in \cref{ValidProofShare}.

@@

For privacy, we require a set of unlinkability properties:%
\label{privacy-properties}
\begin{requirements}[P]
\item\label{PseudonymUnlink} \emph{Pseudonym unlinkability}: given a protest 
  (identifier \cid), protesters Alice and Bob, and a pseudonym \(\pid_b\), the 
  adversary cannot tell if \(\pid_b = \pid_{\text{Alice}}\) or \(\pid_b = 
    \pid_{\text{Bob}}\), except with negligible probability. And similarly with $wid$ if Alice and Bob act as witnesses.
\item\label{ProtestUnlink} \emph{Protest unlinkability}: protesters' pseudonyms 
  (\(\pid_{\cid}, \pid_{\cid'}\)) must be unlinkable between protests (\(\cid, 
  \cid'\)) from the adversary's perspective.
\item\label{WitnessUnlink}\emph{Witness unlinkability}:  witnesses' pseudonyms 
  (\(\wid_{\pid}, \wid_{\pid'}\)) must be unlinkable between protesters 
  (\(\pid, \pid'\)) from the adversary's perspective.
\end{requirements}

### 2021-06-16 paper/verifiability-analysis.tex
Updates data in adversary model

There exists another case of collision that we must prevent.
Consider the situation in which Alice computes \(\pid = \ACprf[_\sk][\cid]\) for some cause identifier \(\cid\) and some witnesses computes \(\wid_1, \dotsc, \wid_n\), with \(\wid_i = \ACprf[_{\sk_i}][\pid]\).
Now, if Alice constructs a manifesto \(m\) such that \(\Hash[m] = \pid\), then \(\wid_1, \dotsc, \wid_n\) would be valid participant identifiers for the protest with manifesto \(m\).
The protocol prevents such use by the fact that \(\pid\) and \(\wid\) are in 
fixed positions in both \[
  \prf_{\wid} = \SPK[\sk_i][\dotsc][\cid, \pid, \wid, t_s, t_s', l]
\] and \[
  \prf_{\pid} = \SPK[\sk_i][\dotsc][\cid, \pid, \wid, t_s, t_s', l],
\] and the two proofs can thus not be confused.
Thus, the verification process differs for the two types of proofs.

@@

\Cref{IndividualVerif} means that Alice and Bob, as participants, can verify 
that their participation proofs (\ie proof shares) are indeed included in the 
computed count.
All proof shares (\ie \(\prf_{\pid, \prtst} = (\cid, \pid, \wid, t_s, t_s', 
  t_e, t_e', l, \corr_\pid, \corr_\wid)\)) are committed to the ledger~\(\TS\) 
and available from a public and permanent storage.
Thus, Alice and Bob can simply check that all of their proof shares are indeed 
there and the security of individual verifiability depends on the properties of 
the ledger (\cf \cref{timestamp}).

@@

\Cref{UniversalVerif} implies that anyone can check the result and that all 
participation proofs counted are legitimate.
As the proof shares are committed and stored publicly, anyone can
download them, verify eligibility (\ie verify \(\corr_\pid,
\corr_{\wid}\)) of the proofs and count them.
Like for individual verifiability, the security of universal verifiability is 
reduced to the properties of the ledger; but universal verifiability also 
depends on the eligibility verification (each proof must be verified as 
eligible to count).

>>>>

There exists another case of collision that we must prevent.
Consider the situation in which Alice computes \(\pid = \ACprf[_{\sk}][\cid]\) 
for some cause identifier \(\cid\) and some witnesses computes \(\wid_1, 
\dotsc, \wid_n\), with \(\wid_i = \ACprf[_{\sk_i}][\pid]\).
Now, if Alice constructs a manifesto \(m\) such that \(\Hash[m] = \pid\), then \(\wid_1, \dotsc, \wid_n\) would be valid participant identifiers for the protest with manifesto \(m\).
The protocol prevents such use by the fact that \(\pid\) and \(\wid\) are in 
fixed positions in both \[
  \prf_{\wid} = \SPK[\sk_i][\dotsc][\cid, \pid, \wid, t_s, t_s', l]
\] and \[
  \prf_{\pid} = \SPK[\sk_i][\dotsc][\cid, \pid, \wid, t_s, t_s', l],
\] and the two proofs can thus not be confused.
Thus, the verification process differs for the two types of proofs.

@@

\Cref{IndividualVerif} means that Alice and Bob, as participants, can verify 
that their participation proofs (\ie proof shares) are indeed included in the 
computed count.
All proof shares (\ie \(\prf_{\pid, \prtst} = (\cid, \pid, \wid, t_s, t_s', 
t_e, t_e', l, \corr_{\pid}, \corr_{\wid})\)) are committed to the 
ledger~\(\TS\) and available from a public and permanent storage.
Thus, Alice and Bob can simply check that all of their proof shares are indeed 
there and the security of individual verifiability depends on the properties of 
the ledger (\cf \cref{timestamp}).

@@

\Cref{UniversalVerif} implies that anyone can check the result and that all 
participation proofs counted are legitimate.
As the proof shares are committed and stored publicly, anyone can
download them, verify eligibility (\ie verify \(\corr_{\pid},
\corr_{\wid}\)) of the proofs and count them.
Like for individual verifiability, the security of universal verifiability is 
reduced to the properties of the ledger; but universal verifiability also 
depends on the eligibility verification (each proof must be verified as 
eligible to count).
